---
title: "家庭動態社會調查主樣本的生活滿意度分數（男女靜態）"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    source_code: embed
---

```{r}
load("cohortmale.Rda")
load("plotmale_cohort.Rda")
```

  Happy 
=======================================

Column 
-------------------------------------

### Male Happiness Group Mean
    
```{r}
graph_male$happy
```

Column
-------------------------------------

### Female Happiness Group Mean

```{r}
graph_female$happy
```

  Life
=======================================

Column
---------------------------------------

### Male Life Group Mean

```{r}
graph_male$life
```

Column
---------------------------------------

### Female Life Group Mean

```{r}
graph_female$life
```

  Health
=======================================

Column
----------------------------------------

### Male Health Group Mean

```{r}
graph_male$health
```

Column
----------------------------------------

### Female Health Group Mean

```{r}
graph_female$health
```

  Shealth
========================================

Column
----------------------------------------

### Male Shealth Group Mean

```{r}
graph_male$Shealth
```

Column
----------------------------------------

### Female Shealth Group Mean

```{r}
graph_female$Shealth
```

  Eco_satisfaction
=========================================
Column
----------------------------------------

### Male Eco_satis Group Mean

```{r}
graph_male$eco_satis
```

Column
----------------------------------------

### Female Eco_satis Group Mean

```{r}
graph_female$eco_satis
```

  Work_satisfaction
===========================================
Column
----------------------------------------

### Male Work_satis Group Mean

```{r}
graph_male$work_satis
```

Column
----------------------------------------

### Female Work_satis Group Mean

```{r}
graph_female$work_satis
```

  Family_satisfaction
==========================================
Column
------------------------------------------

### Male Family_satis Group Mean

```{r}
graph_male$family_satis
```

Column
------------------------------------------

### Female Family_satis Group Mean

```{r}
graph_female$family_satis
```

  Marry_satisfaction
==========================================
Column
------------------------------------------

### Male Marry_satis Group Mean

```{r}
graph_male$marry_satis
```

Column
-----------------------------------------

### Female Marry_satis Group Mean

```{r}
graph_female$marry_satis
```


